---
title: "Developing Data Products - Course Project"
author: "Biju Balachandran"
date: "21 Feb 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Lego Set Visualisation

type: sub-section

This presentation is being created as part of the peer assessment for the coursera developing data products class. The assignment is geared toward ensuring the following concepts were well understood by the students

- **shiny** to build data product application
- **R-Presentation or slidify** to create data product related presentations

## The Application


To display the understanding of using **shiny** to build an application, a simple application called **Lego Set Visualizer** has been developed and deployed at: 
https://bijub21.shinyapps.io/DataProducts_Project/

The application allows the user to:
- Select the inputs like- timelines in year from 1950 to 2016 ,
- No of pieces 
- Set if loego themes from the dataset 
- Select the output to be displayed on the table
- Also has a option to visualise the data


##The Data

The Application uses data from sets.csv

Source code for the project and the data are is available on the 
[GitHub](https://github.com/bijub2110/CreateDataProducts).


### Data

Read Data
```{r}
library(data.table)
data <- fread("./data/sets.csv")
head(data)
```
